\begin{thebibliography}{12}
\section*{Corso}
\bibitem{zaffaroni}
Zaffaroni, A. (2021). \href{https://elearning.unimib.it/course/view.php?id=39146}{Teoria della informazione e della computazione quantistica}. Università degli Studi di Milano - Bicocca.
\section*{Libri}
\bibitem{nielsen}
Nielsen, M. A., Chuang, I. L. (2000). Quantum Computation and Quantum Information. Cambridge University Press.
\bibitem{mermin}
Mermin, N. (2007). Quantum Computer Science: An Introduction. Cambridge University Press.
\section*{Lezioni}
\bibitem{scottaaronson}
Aaronson, S. (2018). \href{https://www.scottaaronson.com/qclec.pdf}{Introduction to Quantum Information Science Lecture Notes}. University of Texas at Austin.
\bibitem{preskill}
Preskill, J. (1997-2020). \href{http://theory.caltech.edu/~preskill/ph219/}{Course Information for Physics and Computer Science on Quantum Computation}. California Institute of Technology.
\section*{Articoli}
\bibitem{surface-code}
Fowler, A., Mariantoni, M., Martinis, J., \& Cleland, A. (2012). Surface codes: Towards practical large-scale quantum computation. Physical Review A, 86(3).
\bibitem{ion-trap1}
Haffner, H., Roos, C., \& Blatt, R. (2008). Quantum computing with trapped ions. Physics Reports, 469(4), 155–203.
\bibitem{ion-trap2}
Bruzewicz, C., Chiaverini, J., McConnell, R., \& Sage, J. (2019). Trapped-ion quantum computing: Progress and challenges. Applied Physics Reviews, 6(2), 021314.
\bibitem{ion-trap3}
Sørensen, A., \& Mølmer, K. (2000). Entanglement and quantum computation with ions in thermal motion. Physical Review A, 62(2).
\bibitem{ion-trap4}
Mølmer, K., \& Sørensen, A. (1999). Multiparticle Entanglement of Hot Trapped Ions. Physical Review Letters, 82(9), 1835–1838.
\bibitem{sup-qubit1}
Krantz, P., Kjaergaard, M., Yan, F., Orlando, T., Gustavsson, S., \& Oliver, W. (2019). A quantum engineer’s guide to superconducting qubits. Applied Physics Reviews, 6(2), 021318.
\bibitem{sup-qubit2}
Kwon, S., Tomonaga, A., Lakshmi Bhai, G., Devitt, S., \& Tsai, J.S. (2021). Gate-based superconducting quantum computing. Journal of Applied Physics, 129(4), 041102.
\bibitem{sup-qubit3}
Girvin, S. M. (2012). Circuit QED: Superconducting Qubits Coupled to Microwave Photons. Oxford University Press.
\end{thebibliography}