\begin{thebibliography}{12}
\section*{Corso}
\bibitem{nucciotti}
Nucciotti, A. (2021). \href{https://elearning.unimib.it/course/view.php?id=39133}{Tecnologie Quantistiche Applicate}. Università degli Studi di Milano - Bicocca.
\section*{Libri}
\bibitem{nielsen}
Nielsen, M. A., Chuang, I. L. (2000). Quantum Computation and Quantum Information. Cambridge University Press.
\bibitem{braginsky}
Braginsky, V., Khalili, F., \& Thorne, K. (1992). Quantum Measurement. Cambridge: Cambridge University Press.
\bibitem{schmidt}
Schmidt, V. V. (1997). The Physics of Superconductors. Introduction to Fundamentals and Applications. Springer Berlin, Heidelberg.
\bibitem{tinkham}
Tinkham, M. (2004). Introduction to Superconductivity. Dover Publications.
\bibitem{feynman}
Feynman, R. (2011). The Feynman Lectures on Physics Vol 3 Quantum Mechanics, Chapter 21. Basic Books.
\bibitem{zagoskin}
Zagoskin, A. (2011). Quantum Engineering: Theory and Design of Quantum Coherent Structures. Cambridge: Cambridge University Press.
\bibitem{chen}
Chen, G., Church, D. A., Englert, B.-G., Henkel, C., Rohwedder, B., Scully, M.O., \& Zubairy, M.S. (2006)
Quantum Computing Devices: Principles, Designs, and Analysis (1st ed.). Chapman and Hall/CRC.
\bibitem{devoret}
Devoret, M.H. (1997). Quantum Fluctuations in Electrical Circuits. In Quantum Fluctuations (Les Houches Session LXIII). Elsevier.

\section*{Tesi}
\bibitem{schuster}
Schuster, D. I. (2007). Circuit Quantum Electrodynamics. PhD Thesis, Yale University.
\bibitem{slichter}
Slichter, D. H. (2011). Quantum Jumps and Measurement Backaction in a Superconducting Qubit. PhD Thesis, University of California, Berkeley.
\bibitem{long}
Long, J. (2014). Superconducting Quantum Circuits for Quantum Information Processing. PhD Thesis, Colorado University.

\section*{Articoli}
\bibitem{quantum-noise}
Clerk, A. A., Devoret, M. H., Girvin, S. M., Marquardt, F., \& Schoelkopf, R. J. (2010). Introduction to quantum noise, measurement, and amplification. Reviews of Modern Physics, 82(2), 1155–1208.
\bibitem{quantum-oscillator}
Caves, C. M., Thorne, K. S., Drever, R. W. P., Sandberg, V. D., \& Zimmermann, M. (1980). On the measurement of a weak classical force coupled to a quantum-mechanical oscillator. I. Issues of principle. Rev. Mod. Phys., 52, 341–392.
\bibitem{ql-linear-amp}
Caves, C. M. (1982). Quantum limits on noise in linear amplifiers. Phys. Rev. D, 26, 1817–1839.
\bibitem{sup-qubit1}
Krantz, P., Kjaergaard, M., Yan, F., Orlando, T., Gustavsson, S., \& Oliver, W. (2019). A quantum engineer’s guide to superconducting qubits. Applied Physics Reviews, 6(2), 021318.
\bibitem{sup-qubit2}
Girvin, S. M. (2012). Circuit QED: Superconducting Qubits Coupled to Microwave Photons. Oxford University Press.
\bibitem{jj}
Martinis, J. M., Devoret, M. H., \& Clarke, J. (1987). Experimental tests for the quantum behavior of a macroscopic degree of freedom: The phase difference across a Josephson junction. Phys. Rev. B, 35, 4682–4698.
\bibitem{sc-q-c}
Wendin, G., \& Shumeiko, V. S. (2005). Superconducting Quantum Circuits, Qubits and Computing.
\bibitem{naghiloo}
Naghiloo, M. (2019). Introduction to Experimental Quantum Measurement with Superconducting Qubits.
\bibitem{martinis-1}
Martinis, J. M., Nam, S., Aumentado, J., \& Urbina, C. (2002). Rabi Oscillations in a Large Josephson-Junction Qubit. Phys. Rev. Lett., 89, 117901.
\bibitem{blais-1}
Blais, A., Huang, R.-S., Wallraff, A., Girvin, S. M., \& Schoelkopf, R. J. (2004). Cavity quantum electrodynamics for superconducting electrical circuits: An architecture for quantum computation. Phys. Rev. A, 69, 062320.
\bibitem{koch-1}
Koch, J., Yu, T. M., Gambetta, J., Houck, A. A., Schuster, D. I., Majer, J., \& Schoelkopf, R. J. (2007). Charge-insensitive qubit design derived from the Cooper pair box. Phys. Rev. A, 76, 042319.
\bibitem{walter-1}
Walter, T., Kurpiers, P., Gasparinetti, S., Magnard, P., Potoč, A., Salathé, Y., \& Wallraff, A. (2017). Rapid High-Fidelity Single-Shot Dispersive Readout of Superconducting Qubits. Phys. Rev. Applied, 7, 054020.
\bibitem{dassonneville-1}
Dassonneville, R., Ramos, T., Milchakov, V., Planat, L., Dumur, É., Foroughi, F., \& Buisson, O. (2020). Fast High-Fidelity Quantum Nondemolition Qubit Readout via a Nonperturbative Cross-Kerr Coupling. Phys. Rev. X, 10, 011045.
\end{thebibliography}